The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-21 src/ms.tex
add pandas and geopandas citations
Font change for 2dfdr

As many of the surveys hosted by Data Central are spectroscopic surveys from the
AAT, \package{specutils} is heavily used to standardize the variety of encodings
of spectroscopic data into a form easily readable and visualizable by many
standard tools (such as \package{ds9} or \package{splat}). Data Central has
upstreamed into \package{specutils} loaders for all hosted spectra, including
2dfdr-reduced spectra from the AAT Archive, and strongly encourages other
archives to provide loaders for their data to further the reuse of existing archival
data.

@@

\software{\package{astropy} \citep{astropy:2013, astropy:2018},
          \package{numpy} \citep{numpy:nature},
          \package{scipy} \citep{scipy},
          \package{matplotlib} \citep{matplotlib},
          \package{Cython} \citep{cython}.
          % \package{photutils} \citep{photutils},
          % \package{specutils} \citep{specutils},
          % \package{regions} \citep{regions},
          % \package{gwcs} \citep{gwcs},
          % \package{synphot} \citep{synphot},
          % \package{ASDF} \citep{ASDF}.
          % \package{SOFA} \citep{sofa},
          % \package{ERFA} (\citealt{erfa})
          }

>>>>

As many of the surveys hosted by Data Central are spectroscopic surveys from the
AAT, \package{specutils} is heavily used to standardize the variety of encodings
of spectroscopic data into a form easily readable and visualizable by many
standard tools (such as \package{ds9} or \package{splat}). Data Central has
upstreamed into \package{specutils} loaders for all hosted spectra, including
\package{2dfdr}-reduced spectra from the AAT Archive, and strongly encourages other
archives to provide loaders for their data to further the reuse of existing archival
data.

@@

\software{\package{astropy} \citep{astropy:2013, astropy:2018},
          \package{Cython} \citep{cython}.
          \package{geopandas} \citep{geopandas},
          \package{matplotlib} \citep{matplotlib},
          \package{numpy} \citep{numpy:nature},
          \package{pandas} \citep{pandas, pandas2},
          \package{scipy} \citep{scipy}.
          % \package{photutils} \citep{photutils},
          % \package{specutils} \citep{specutils},
          % \package{regions} \citep{regions},
          % \package{gwcs} \citep{gwcs},
          % \package{synphot} \citep{synphot},
          % \package{ASDF} \citep{ASDF}.
          % \package{SOFA} \citep{sofa},
          % \package{ERFA} (\citealt{erfa})
          }
